Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-02-16 doc/main_jfm.tex
yny 6th today

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
decreases and $b$ are}
%over a range of shear rates which is 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d). 
%
\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

>>>>

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Two-Dimensional Hydrodynamics of a Janus Particle Vesicle}
%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
decreases and $b$ are}
%over a range of shear rates which is 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
%\subsubsection{Membrane Ruptures}
%\begin{figure}
%\centering
%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%%\includegraphics[height=2in]{N58_rupt_0.pdf}
%%\includegraphics[height=2in]{N58_rupt_200.pdf}
%\\
%%\includegraphics[height=2in]{N58_rupt_400.pdf}
%%\includegraphics[height=2in]{N58_rupt_600.pdf}
%  \caption{\label{figure8} Tank-treading leads to membrane rupture for
%  large shear rates.} 
%\end{figure}
%A temporary fissure or a complete membrane rupture can occur at large
%shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
%when suspended in a shear flow. For $\chi = 0.1$, starting with a
%circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
%background flow and fissures appear in the bilayer structure in multiple
%locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
%ruptured vesicles form two planar micelles which are eventually carried
%off by the flow (Figure~\ref{figure8}d). 
%%
%\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d). 
%

\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
  and did not rupture whenever $\chi < \chi_*.$ 
  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
  To further quantify the competition between shear and attraction,
  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
  A 5 \% decrease in the particle radius $c$ gave a -9.55 \% decrease in $\chi_*$
  and a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.
  These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Here $\text{Ca}$ would be approximately $1.7$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/\kappa$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $\kappa$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
  \[
  \kappa = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $\kappa \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
